The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-18 dit-paper_ieee.tex

		The following necessary and sufficient condition of feasibility
		based on the DBF is given in \cite{baruah1999generalized}:

		\begin{theorem}
			\begin{equation}
				\begin{array}{c}
					\tau \: \text{is feasible}  \iff
					\dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
				\end{array}
			\end{equation}
		\end{theorem}

        Indeed, if there exists values of $t_1$ and $t_2$ such that $\dbf{t_1, t_2} > t_2 - t_1$, it means that more than $t_2 - t_1$ unit of computation have to be done in $t_2 - t_1$ unit of time. Therefore the system is unfeasible.

@@

		The DBF test gives us a list of inequations on the WCET values of the task set
		which, taken together, are a necessary and sufficient condition of feasibility. They
		can all be written in the following way:
		\begin{equation}
			\sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
		\end{equation}
		Note that for given values  of $(t_1, t_2)$, the $n_i(t_1, t_2)$ are
		constant (w.r.t. the $C_i$). Those inequations are thus indeed linear.

>>>>

		The following necessary and sufficient condition of feasibility
		based on the DBF is given in \cite{baruah1999generalized}:
		\begin{theorem}
			\begin{equation*}
				\begin{array}{c}
					\tau \: \text{is feasible}  \iff
					\dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall t_1, t_2 \mid  0 \leq t_1 \leq t_2
				\end{array}
			\end{equation*}
		\end{theorem}
        Indeed, if there exists values of $t_1$ and $t_2$ such that $\dbf{t_1, t_2} > t_2 - t_1$, it means that more than $t_2 - t_1$ unit of computation have to be done in $t_2 - t_1$ unit of time. Therefore the system is unfeasible.

@@

		The DBF test gives us a list of inequations on the WCET values of the task set
		which, taken together, are a necessary and sufficient condition of feasibility. They
		can all be written in the following way:
		\begin{equation}
			\sum_{i=1}^{n}  n_i(t_1, t_2) \cdot C_i \leq t_2 - t_1 \; \forall t_1,t_2 \mid 0 \leq t_1 \leq t_2
		\end{equation}
		Note that for given values  of $(t_1, t_2)$, the $n_i(t_1, t_2)$ are
		constant (w.r.t. the $C_i$). Those inequations are thus indeed linear.
